SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-09-10 scipy-1.0/paper.tex
MAINT: reviewer comment re: GPUs, etc.
* both Nature Methods reviewers requested clarification
regarding SciPy's stance on staying relevant with GPUs
and distributed computing

* briefly mention that while these were out of scope
at the 1.0 release point, we now have an explicit
example of experimental GPU backend support in scipy.fft,
to be detailed in a future report

In terms of software systems and architecture, SciPy's scope matches NumPy's:
algorithms for in-memory computing on single machines, with support for a wide
range of data types and process architectures. Distributed computing and support
for graphics processing units (GPUs) are explicitly out of scope.

@@

The position that SciPy occupies near the
foundation of the scientific Python ecosystem is such that adoption of new
languages or major dependencies is generally unlikely---our choices are strongly
driven by long-term stability. GPU acceleration, new transpiling libraries, and
the latest JIT compilation approaches (i.e.,
Numba\cite{Lam:2015:NLP:2833157.2833162}) are very powerful, but currently fall
outside the remit of the main SciPy library. That said, we have recently
increased our efforts to support compatibility with some of these options, and
having our full test suite pass with the PyPy JIT
compiler\cite{Bolz:2009:TMP:1565824.1565827} is now a requirement in our
development workflow.

>>>>

In terms of software systems and architecture, SciPy's scope matches NumPy's:
algorithms for in-memory computing on single machines, with support for a wide
range of data types and process architectures. Distributed computing and support
for graphics processing units (GPUs) were explicitly out of scope at the 1.0
release point, but this has been revised in our roadmap at the time of writing
(see below).

@@

The position that SciPy occupies near the
foundation of the scientific Python ecosystem is such that adoption of new
languages or major dependencies is generally unlikely---our choices are strongly
driven by long-term stability. GPU acceleration, new transpiling libraries, and
the latest JIT compilation approaches (i.e.,
Numba\cite{Lam:2015:NLP:2833157.2833162}) are very powerful, but have traditionally fallen
outside the remit of the main SciPy library. That said, we have recently
increased our efforts to support compatibility with some of these options, and
while the exact approach we will adopt across the entire library remains unclear,
we do now have a concrete implementation of a submodule that allows for the experimental
use of multiple backends such as GPU-tractable data structures in the new
\texttt{scipy.fft}. This will be described in detail in a future report.
